Topic Scores

### 2019-02-19 Topic Scores.Rmd
comments

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---

```{r setup, include=FALSE}
load("Output/LDA.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/LDA_overview_5.RDATA")
```

## function get gamma and beta
```{r getting functions}
get_beta <- function(results){

@@

```
##getting gamma and beta data 
```{r getting beta and gamma}
beta_descriptions <- LDA_overview_5 %>%
  get_beta

gamma_descriptions <- LDA_overview_5 %>%
  get_gamma
```

## simulating students and key words
```{r student simulation}
set.seed(126)

terms <- unique(beta_descriptions$term)

student <- list()
student$kw <- c("international", "economic", "conflict", "develop", "policy") #sample(terms, 5)
```

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_descriptions%>%
  filter(term %in% student$kw) %>%
  group_by(topic)%>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))%>%
  ungroup()%>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b) %>%
  arrange(desc(B_score))

@@

student$course_score
```
###Other comparison functions
```{r other functions}
#
##Binary

>>>>

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---
#Set up
##Libraries
```{r libraries}
```
##Raw Data
```{r setup, include=FALSE}
#
##d_course and d_transcript
load("Output/data_pillar_1.RDATA")

#
##LDA_models
load("Output/LDA_overview.RDATA")

#
##Topic Models test for ideal number of topics
load("Output/LDA_ntopics_description.RDATA")
load("Output/LDA_ntopics_overview.RDATA")

## Getting Functions (gamma and beta) 
```{r getting functions}
get_beta <- function(results){

@@

##Getting applied (gamma and beta) 
```{r getting beta and gamma}
beta_descriptions <- LDA_model %>%
  get_beta

gamma_descriptions <- LDA_model %>%
  get_gamma
```

## simulating students and key words
```{r student simulation}
terms <- unique(beta_descriptions$term)

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy") #sample(terms, 5)
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
```

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_descriptions%>%
  filter(term %in% student$kw_climate) %>%
  group_by(topic)%>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))%>%
  ungroup()%>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b) %>%
  arrange(desc(B_score))

@@

View(student$course_score)
```
###Other comparison functions
```{r other functions}
#
##Binary
product <- function(a = gamma, b = B_score){
  X = a*b
}
